---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![stability-unstable](https://img.shields.io/badge/stability-unstable-yellow.svg)](https://github.com/joethorley/stability-badges#unstable)
[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/subfoldr.svg?branch=master)](https://travis-ci.org/poissonconsulting/subfoldr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/subfoldr?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/subfoldr)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/subfoldr/master.svg)](https://codecov.io/github/poissonconsulting/subfoldr?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/subfoldr)](https://cran.r-project.org/package=subfoldr)

# subfoldr

`subfoldr` is an R package to orchestrate the saving and loading of 
data, tables, plots, templates and objects 
to a directory and the generation of markdown results

## Installation

`subfoldr` can be installed from GitHub

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("poissonconsulting/subfoldr")
```

or the Poisson R Archive Network ([PoisRAN](https://github.com/poissonconsulting/drat))

```{r poisran-installation, eval = FALSE}
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("subfoldr")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/subfoldr/issues).

[Pull requests](https://github.com/poissonconsulting/subfoldr/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/poissonconsulting/subfoldr/blob/master/CONDUCT.md). 
By participating in this project you agree to abide by its terms.
